Improving content discovery through combining linked data and data mining techniques

### 2016-04-24 report/chapters/03-design.tex
Halfway through chapter 4

\chapter{System Design}

@@

\section{Data Pipeline}

@@

\subsection{Identity Graph}

@@

In this section, a data pipeline was inductively built up from a base,
identify pipeline with suggestions for potential improvements in different
stages. An application of all the ideas discussed so far might look like
that depicated in Figure\ref{fig:maximal-pipeline}.

@@

The pipeline visualisation in Figure\ref{fig:maximal-pipeline} shows strong
potential for parallisation of parts of the data pipeline. In particular, the
enrichment and extraction stages comprise potentially several distinct
strategies that can run entirely independently, with a set union of the graphs
bringing the respective outputs together.

This pattern has the appearance of benefitting from the
MapReduce\cite{dean2008mapreduce} model and we can consider frameworks such
as Apache Spark\cite{zaharia2010spark} to handle distributing the data pipeline
over a cluster of servers.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=\linewidth]{diagrams/component2.png}
  \end{center}
  \caption{Component diagram expanded with technology choices\label{fig:component}}
\end{figure}

>>>>

\chapter{System Design}
\label{chp:design}

@@

\section{Data Pipeline}
\label{sec:design-pipeline}

@@

\subsection{Identity Graph}
\label{sec:identity-graph}

@@

In this section, a data pipeline was inductively built up from a base,
identify pipeline with suggestions for potential improvements in different
stages. An application of all the ideas discussed so far might look like
that depicated in Figure~\ref{fig:maximal-pipeline}.

@@

\section{Architecting for Experimentation}
